%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Web Developer \& Technical Head   |  {\href{https://plinth.in}{ Website Link}}}  % Job title
    {Plinth'19} % Organization
    {Jaipur, Rajasthan} % Location
    {Aug. 2018 - Jan. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a compelete website for LNMIIT's Techfest.}
        \item {The website managed the events, participants, registrations, payment, and notifications.}
        \item {Integrated payment portal, automatic receipt generation, user dashboard and mail notification.}
        \item {Made online quizzing event Cryptex's platform, comprising of leaderboard and admin panel.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Summer'18 Academic Internship} % Job title
    {LUSIP} % Organization
    {Jaipur, Rajasthan} % Location
    {May. 2018 - July. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Under the guidance of Dr. Preety Singh, HOD CSE Dept., LNMIIT, I completed my project on "Driver Fatigue Detection using Video Processing Techniques".}
        \item {A computer vision system that can automatically detect driver drowsiness by tracking closing of eyes and yawing in a real-time video stream and then alert if the driver appears to be drowsy.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {General Body Member} % Job title
    {Science \& Technology Council, LNMIIT Students' Gymkhana} % Organization
    {Jaipur, Rajasthan} % Location
    {Apr. 2017 - May. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Being the general body member, my task was to look after the technical events organised in LNMIIT and to work with G.Sec. Sci and Tech. for improving the technical environment in our college campus.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Fest Manager} % Job title
    {Plinth'18} % Organization
    {Jaipur, Rajasthan} % Location
    {Jun. 2017 - Jan. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I was responsible for managing the operations of whole fest. In addition to this,I also worked in sponsorship team.}
      \end{cvitems}
    }

%---------------------------------------------------------
%   \cventry
%     {Freelance Penetration Tester} % Job title
%     {SAMSUNG Electronics} % Organization
%     {S.Korea} % Location
%     {Sep. 2013, Mar. 2011 - Oct. 2011} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Conducted penetration testing on SAMSUNG KNOX, which is solution for enterprise mobile security.}
%         \item {Conducted penetration testing on SAMSUNG Smart TV.}
%       \end{cvitems}
%       %\begin{cvsubentries}
%       %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
%       %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
%       %\end{cvsubentries}
%     }

%---------------------------------------------------------
\end{cventries}
