%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {\href{https://github.com/nimbus1212/driver_fatigue_detection}{Project Link}}
    {Driver Fatigue Detection System Using OpenCV} % Event
    {Jaipur, Rajasthan} % Location
    {May. 2018 - Jul. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {This system can detect and track user's eyes and mouth and alert when the user is feeling drowsy using video processing techniques.}
      \end{cvitems}
    }
    
  \cventry
    {\href{https://github.com/nimbus1212/paper.lnmiit}{Project Link}}
    {Paper.LNMIIT} % Event
    {Jaipur, Rajasthan} % Location
    {Sep. 2017 - Nov. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {A team project under Cybros open-source initiative.}
        \item {It is the collection of question papers for all courses taught at LNMIIT for all available years.}
      \end{cvitems}
    }
    
   \cventry
    {Got an A grade in Design Lab}
    {6-bit DAC Power Supply using Arduino} % Event
    {Jaipur, Rajasthan} % Location
    {Jul. 2017 - Dec. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {This power supply can be used in controlling the load of appliances such as cooling fans, low-wattage heaters, thermostats, low-wattage light sources, small electrical toys and test benches for loudspeakers, whose voltage can be controlled in small steps and is capable of providing current of more than 1A.}
        \item {Using the seven segment display, the output voltage was shown.   }
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
